Phenotypic evolution is less constrained in complex food webs

### 2018-09-25 manuscript/manuscript.tex
lots of progress in analysis

\documentclass[11pt]{article}
\usepackage[sc]{mathpazo} %Like Palatino with extensive math support
\usepackage{fullpage}
\usepackage[authoryear,sectionbib,sort]{natbib}
\linespread{1.7}
\usepackage[utf8]{inputenc}
\usepackage{lineno}
\usepackage{titlesec}
\titleformat{\section}[block]{\Large\bfseries\filcenter}{\thesection}{1em}{}
\titleformat{\subsection}[block]{\Large\itshape\filcenter}{\thesubsection}{1em}{}
\titleformat{\subsubsection}[block]{\large\itshape}{\thesubsubsection}{1em}{}
\titleformat{\paragraph}[runin]{\itshape}{\theparagraph}{1em}{}[. ]\renewcommand{\refname}{Literature Cited}

@@

\begin{table}[h]
\caption{Table for Alpha Regression coefficients}
\label{Table:Alphas}
\centering
\begin{tabular}{lcc}
                                                                           \\ \hline
                       & \multicolumn{2}{c}{Food web (Estimate [95\% CI])} \\
\textbf{Coefficient}   & \textbf{Complex} & \textbf{Simple}                \\ \hline
$Diam$                 &  [ - ] &  [ - ] \\
$Clutch$               &  [ - ] &  [ - ] \\
$Pref$                 &  [ - ] &  [ - ] \\
$Diam^2$               &  [ - ] &  [ - ] \\
$Clutch^2$             &  [ - ] &  [ - ] \\
$Pref^2$               &  [ - ] &  [ - ] \\
$Diam:Clutch$          &  [ - ] &  [ - ] \\
$Diam:Pref$            &  [ - ] &  [ - ] \\
$Clutch:Pref$          &  [ - ] &  [ - ]              \\ \hline
\end{tabular}
\bigskip{}
\\
{\footnotesize Note: Table titles should be short. Further details should go in a `notes' area after the tabular environment, like this. $^a$ Okapis are not native to Chicago, but they are to be met with in both of the major Chicagoland zoos.}
\end{table}

\begin{table}[h]
\caption{Table for \textit{Iteomyia} Selection Gradients}
\label{Table:Gradients}
\centering
\begin{tabular}{lcc}
                                                                                  \\ \hline
                                  & \multicolumn{2}{c}{Food web (Estimate [95\% CI])} \\
\textbf{Selection gradient}       & \textbf{Complex} & \textbf{Simple}            \\ \hline
$\beta_{Diam}$                    &  [ - ] &  [ - ] \\
$\beta_{Clutch}$                  &  [ - ] &  [ - ] \\
$\beta_{Pref}$                    &  [ - ] &  [ - ] \\
$\gamma_{Diam,Diam}$              &  [ - ] &  [ - ] \\
$\gamma_{Clutch,Clutch}$          &  [ - ] &  [ - ] \\
$\gamma_{Pref,Pref}$              &  [ - ] &  [ - ] \\
$\gamma_{Diam,Clutch}$            &  [ - ] &  [ - ] \\
$\gamma_{Diam,Pref}$              &  [ - ] &  [ - ] \\
$\gamma_{Clutch,Pref}$            &  [ - ] &  [ - ]            \\ \hline
\end{tabular}
\bigskip{}
\\
{\footnotesize Note: Table titles should be short. Further details should go in a `notes' area after the tabular environment, like this. $^a$ Okapis are not native to Chicago, but they are to be met with in both of the major Chicagoland zoos.}
\end{table}

@@

\begin{figure}[h!]
%\includegraphics{horn-of-okapi}
\caption{Figure legends can be longer than the titles of tables. However, they should not be excessively long.}
\label{Fig:OkapiHorn}
\end{figure}

>>>>

\documentclass[11pt]{article}
\usepackage[sc]{mathpazo} %Like Palatino with extensive math support
\usepackage{graphicx} % for organizing figures
\usepackage{fullpage}
\usepackage[authoryear,sectionbib,sort]{natbib}
\linespread{1.7}
\usepackage[utf8]{inputenc}
\usepackage{lineno}
\usepackage{titlesec}
\titleformat{\section}[block]{\Large\bfseries\filcenter}{\thesection}{1em}{}
\titleformat{\subsection}[block]{\Large\itshape\filcenter}{\thesubsection}{1em}{}
\titleformat{\subsubsection}[block]{\large\itshape}{\thesubsubsection}{1em}{}
\titleformat{\paragraph}[runin]{\itshape}{\theparagraph}{1em}{}[. ]\renewcommand{\refname}{Literature Cited}

@@

\begin{table}[h]
\caption{Table for \textit{Iteomyia} Selection Gradients}
\label{Table:Gradients}
\centering
\begin{tabular}{lcc}
                                                                                  \\ \hline
                                  & \multicolumn{2}{c}{Food web (Estimate [95\% CI])} \\
\textbf{Selection gradient}       & \textbf{Complex} & \textbf{Simple}            \\ \hline
$\beta_{Diam}$                    & 0.47 [0.36-0.58] & 0.29 [0.23,0.37] \\
$\beta_{Clutch}$                  & 0.06 [-0.04,0.17] & -0.13 [-0.25,-0.04] \\
$\beta_{Pref}$                    & -0.24 [-0.36,-0.11] & -0.15 [-0.23,-0.07] \\
$\gamma_{Diam,Diam}$              & 0.13 [0.00,0.26] & 0.08 [0.00,0.16] \\
$\gamma_{Clutch,Clutch}$          & -0.10 [-0.25,0.04] & -0.06 [-0.16,0.02] \\
$\gamma_{Pref,Pref}$              & 0.39 [0.02,0.81] & -0.32 [-0.63,-0.03] \\
$\gamma_{Diam,Clutch}$            & -0.08 [-0.16,0.01] & -0.05 [-0.10,0.01] \\
$\gamma_{Diam,Pref}$              & -0.08 [-0.19,0.02] & -0.05 [-0.12,0.01] \\
$\gamma_{Clutch,Pref}$            & 0.04 [-0.06,0.13] & 0.02 [-0.04,0.08]            \\ \hline
\end{tabular}
\bigskip{}
\\
{\footnotesize Note: Table titles should be short. Further details should go in a `notes' area after the tabular environment, like this. $^a$ Okapis are not native to Chicago, but they are to be met with in both of the major Chicagoland zoos.}
\end{table}

@@

%Path relative to the main .tex file 
\graphicspath{ {../analyses/reproduce_analyses_files/figure-html/} }

\begin{figure}[h!]
\includegraphics{Univariate-Fitness-Landscapes-1.png}
\caption{Selection gradients acting on \texit{Iteomyia} traits in complex vs. simple food webs. Each panel corresponds to a different phenotypic trait: chamber diameter (A); clutch size (B); and female preference (C). Solid lines represent the estimated gradients in complex (orange) and simple (blue) food webs. Transparent lines represent bootstrapped replicates (n=100) to show the uncertainty in estimated gradients. Note that only 100 bootstraps are displayed here, but that inferences are based on 1,000 bootstrapped samples.}
\label{Fig:FL_1D}
\end{figure}

\begin{figure}[h!]
\includegraphics{Multivariate-Fitness-Landscapes-1.png}
\caption{Fitness landscapes of gall traits in complex vs. simple food webs. Each panel corresponds to a different combination of traits: clutch size and chamber diameter (A); clutch size and female preference (B); female preference and chamber diameter (C). Note that traits for all plots range 1 SD below and above the mean (=0).}
\label{Fig:FL_2D}
\end{figure}
